Thermodynamic fragments for magic states in quantum computation

### 2021-03-24 notes/notes.tex
Fixed appendices, except for unital fragment appendix. What do we include there / what do we get rid of?

>>>>

\section{Area monotone}\label{app:areamono}

\nick{I don't believe in the area monotone - should we keep?}

\begin{figure}[h]%
    \centering
    \subfigure[][]{%
    \label{fig:test1}%
    \includegraphics[height=3cm]{figs/negmasking_rho_strange_lc.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:test2}%
    \includegraphics[height=3cm]{figs/negmasking_rho_strange_meas.pdf}
    %\caption{Zero state $\ketbra{0}{0}$}%
    }
    \caption{\subref{fig:test1} Lorenz curve of $p\ketbra{\rm{S}} + (1-p) \frac{1}{d}\id$ for $p$ given in the legend.\subref{fig:test2} Different measures for the states on the left. \\
    \nick{can replace~\cref{fig:lctoy} with a more informative version of this figure}
    }%
    \label{fig:test}
\end{figure}

Let $L_{>1}$ be the set of points on the Lorenz curve $\lc{\rho}{\sigma}(k)$ that lie above $1$ of state $\rho$ in the $\sigma$--fragment. 
If $\rho$ is a free state, $L_{>1}$ is empty and $\A_\sigma(\rho) = 0$. 
Otherwise, $\A_\sigma(\rho) > 0$ and it can be calculated exactly using the trapezium rule or the shoelace formula. 
Let $k$ be the index of the first point $\left(x_k, \lc{\rho}{\sigma}(k)\right)$ lying above $1$. 
Then $L_\rho(k)$ crosses $1$ at
\begin{equation}
	x_{\rm{int}} = x_k - \frac{x_k - x_{k-1}}{\lc{\rho}{\sigma}(k) - \lc{\rho}{\sigma}(k-1)}\lc{\rho}{\sigma}(k),\vspace{10pt}
\end{equation}
as well as at $\left(x_d, \lc{\rho}{\sigma}(d)\right) = (1,1)$

Now we can define
\begin{equation}
L_{>1}^+ = \{ (x_i, y_i) \}_{0 \leq i \leq n}
\end{equation}
such that it contains the initial point of intersection $(x_0, y_0) \equiv (x_{n+1}, y_{n+1}) \coloneqq (x_{\rm{int}}, 1)$, all points $(x_i, y_i)$, labelled by $i=1,\dots,n-1$ that lie above $y=1$ contained in $L_{>1}$ and finally the second point of intersection $(x_n, y_n) = (1,1)$.
Then, 
\begin{equation}
	\A_\sigma(\rho) = \frac{1}{2} \sum\limits_{i=0}^n (x_{i+1} y_i - x_i y_{i+1}).
\end{equation}

We note that single-copy Lorenz curves are additive in noise, 
\begin{equation}
	\lc{(1-\epsilon)\rho + \epsilon\sigma}{\sigma} = (1-\epsilon)\lc{\rho}{\sigma} + \epsilon\lc{\sigma}{\sigma},
\end{equation}
for any $\sigma, \rho$.
This is not true for higher number of copies.

\nick{In particular}, it can be used in the discussion of standard Lorenz curves to set the necessary constraints,
\begin{align}
L\left(x_{I'(0, m'_{0}, 9^{n-n'})}\right) &\geq L\left(x_{I'(0, m'_{0}, 9^{n-n'})}\right), \nonumber\\
L\left(x_{I'(1, m'_{1}, 9^{n-n'})}\right) &\geq L\left(x_{I'(1, m'_{1}, 9^{n-n'})}\right), \nonumber\\
&\vdotswithin{=} \nonumber\\
L\left(x_{I'(n', m'_{r}, 9^{n-n'})}\right) &\geq L\left(x_{I'(n', m'_{n'}, 9^{n-n'})}\right), \nonumber
\end{align}
where $x_{I'(0, m'_{0}, 9^{n - n'})}, x_{I'(1, m'_{1}, 9^{n - n'})}, \dots, x_{I'(n', m'_{n'}, 9^{n - n'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')^{\otimes n'}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).

\section{Stabilizer proof details}
